
```{r {{id}}-setup}
if (interactive()) {
  this_map <- sample(c("nara", "bosw", "bak","gras","all"), 1)
} else {
  this_map <- "{{id}}"
}
title <- ttl[[this_map]]
mapdata1 <- data[[str_c(this_map, "2013")]]$valid_eng
refdata1 <- as.factor(points_id$lu13oord_eng)
mapdata2 <- data[[str_c(this_map, "2016")]]$valid_eng
refdata2 <- as.factor(points_id$lu16oord_eng)
maparea <- area[[this_map]]
```
## Evaluation of `r title`

This section evaluates `r as.character(title)` from 2013 and 2016 and also evaluates how well it captures land use changes.

### Accuracy of land use in the maps

#### Map of 2013
```{r {{id}}-time1accuracy, include=FALSE}
source(find_root_file("src/NCA_functions.R", 
                      criterion = has_file("NCA_validatingextend.Rproj")))
res1 <- CalculateAccuracy(mapdata1, refdata1)

```

The overall accuracy is `r round(100*unname(res1$overall['Accuracy']), digits = 2)`%. Table \@ref(tab:{{id}}-accuracybylu1) shows several accuracy measures for each of the land uses separately. The users accuracy (sensititvity) and producers accuracy (specificity) is also shown in Figure \@ref(fig:{{id}}-userproducer).

```{r {{id}}-accuracybylu1, include=TRUE}
t(res1$byClass) %>% 
  kable(caption = str_c("Accuracy by land use for 2013 for ", title, ". "),
        row.names = TRUE,
        col.names = str_remove(rownames(res1$byClass), "Class: "),
        booktabs = TRUE)
```

#### Map of 2016

```{r {{id}}-time2accuracy, include=FALSE}
res2 <- CalculateAccuracy(mapdata2, refdata2)

```

The overall accuracy is `r round(100*unname(res2$overall['Accuracy']), digits = 2)`%. Table \@ref(tab:{{id}}-accuracybylu2) shows several accuracy measures for each of the land uses separately. 
```{r {{id}}-accuracybylu2, include=TRUE}
t(res2$byClass) %>% 
  kable(caption = str_c("Accuracy by land use for 2016 for ", title, ". "),
        row.names = TRUE,
        col.names = str_remove(rownames(res1$byClass), "Class: "),
        booktabs = TRUE) 
```

Figure \@ref(fig:{{id}}-userproducer) shows the user and producer accuracy for each of the landuse categories and for each of the years.

```{r {{id}}-userproducer, include=TRUE, fig.cap=str_c("UA and PA for each of the land uses and for each of the years for ",title,". ")}
data.frame(users = c(res1$byClass[,5], res2$byClass[,5]),
                producers = c(res1$byClass[,6], res2$byClass[,6]),
                lu = rep(str_remove(rownames(res1$byClass), "Class: "),2),
                year = c(rep(2013, nrow(res1$byClass)), rep(2016, nrow(res2$byClass)))) %>%
  mutate(lu = as.factor(lu),
         year = as.factor(year)) %>%
  ggplot() +
  geom_point(aes(x = users, y = producers, color = lu, shape = year)) +
  scale_color_discrete(name = "land use") +
  xlab("user's accuracy (precision)") +
  ylab("producer's accuracy (recall)") +
  theme_bw()
```

### Accuracy of land use changes 

Apart from the accuracy of the map itself, it is also important to know the accuracy of the changes over time. As there are `r nlevels(mapdata1)` land use categories (`r str_c(levels(mapdata1), collapse = ", ")`),  there are  `r nlevels(mapdata1)*nlevels(mapdata1)` possible changes that may happen over time. Table \@ref(tab:{{id}}-observedchanges) shows the number of times each of the types of changes is observed on the map and in the reference dataset. Overall, the map showed land use changes in `r sum(mapdata1 != mapdata2)` cells (`r round(sum(mapdata1 != mapdata2)/length(mapdata1)*100, digits = 2)`%) while the reference dataset showed a change in land use in `r sum(refdata1 != refdata2)` out of the `r length(refdata1)` cells (`r round(sum(refdata1 != refdata2)/length(refdata1)*100, digits = 2)`%).

```{r {{id}}-observedchanges, include=TRUE}
observed_changes <- data.frame(map = as.factor(str_c(mapdata1, mapdata2, sep = "-")),
                               ref = as.factor(str_c(refdata1, refdata2, sep = "-")),
                               mapchange = as.factor(ifelse(mapdata1 == mapdata2, 
                                                  "No change", "Change")),
                               refchange = as.factor(ifelse(refdata1 == refdata2, 
                                                  "No change", "Change"))) %>%
  mutate(map = factor(map, levels = sort(unique(c(levels(map),levels(ref))))),
         map = factor(map, levels = levels(map))) 
observed_changes %>%
  pivot_longer(cols = 1:2, names_to = "type", values_to = "change") %>%
  group_by(change) %>%
  summarize(map = sum(type == "map"),
            ref = sum(type == "ref")) %>%
  ungroup() %>%
  kable(caption = str_c("Observed land used changes on the map and in the reference data between 2013 and 2016 for ", title, ". "),
              col.names = c("Type of change", "Map","Reference"),
        booktabs = TRUE) 
```

```{r {{id}}-observedchanges2, include=TRUE}
reschange1 <- CalculateAccuracy(observed_changes$map, observed_changes$ref)
reschange2 <- CalculateAccuracy(observed_changes$mapchange, observed_changes$refchange)
```

The overall accuracy is `r round(100*unname(reschange1$overall['Accuracy']), digits = 2)`%. Table \@ref(tab:{{id}}-accuracybyluchange) shows several accuracy measures for each of the land use changes separately.

If we look at the land use change as a 0/1 variable (change or no change) in stead of considering all different types of land use changes, the overall accuracy increases to `r round(100*unname(reschange2$overall['Accuracy']), digits = 2)`%. Table \@ref(tab:{{id}}-accuracychange) shows the confusion matrix and Table \@ref(tab:{{id}}-accuracychange2) shows all accuracy measures.

```{r {{id}}-accuracybyluchange, include=TRUE}
A <- reschange1$byClass[,c(1,2,5,6)] 
rownames(A) <- str_remove(rownames(A), "Class: ")
A %>% kable(caption = str_c("Accuracy of land use changes  for ", title, " (only some accuracy measures are shown but others can be requested)."),
        row.names = TRUE,
        booktabs = TRUE) 
```

```{r {{id}}-accuracychange, include=TRUE}
reschange2$table %>% kable(caption = str_c("Confusion matrix for land use changes, only comparing change / no change for ", title, ". "),
        row.names = TRUE,
        booktabs = TRUE) 
```

```{r {{id}}-accuracychange2, include=TRUE}
reschange2$byClass %>% 
  kable(caption = 
          str_c("Accuracy of land use changes, only comparing change / no change for ",
                title, ". "),
        booktabs = TRUE) 
```

#### Confidence intervals on the area that changed

```{r {{id}}-uncertaintyarea, include=TRUE}
ov <- Validationuncertainty(ma = as.data.frame.matrix(reschange1$table), maparea = maparea$area, pixelsize = 0.01)#each cell is 100 square meters = 0.01ha
```
```{r {{id}}-uncertaintyareabar, include=TRUE, fig.cap = str_c("Estimated changed area (bars) with confidence intervals versus changed area according to the map (dots) for ", title, ". Asterisks identify area changes that were significantly different from zero.")}
PlotValidationData(ov)
```
